The connection between star formation rate and dark matter halo mass during reionization

### 2015-09-04 paper/ms.tex
Tables.

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.07_{-0.06}^{+0.10}$ & 0.03 & $17.81_{-0.08}^{+0.12}$ & 0.02  \\
$\log_{10}(M_0/M_{\odot})$ & $11.19_{-0.03}^{+0.67}$ & 0.07 & $11.12_{-0.24}^{+0.58}$ & 0.06  \\
$\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Willott data with and without 
dust attenuation over 64 small boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Willott_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.03 & $17.81_{-0.16}^{+0.22}$ & 0.06  \\
$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.07 & $11.82_{-0.32}^{+1.02}$ & 0.13  \\
$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.18 & $ 0.91_{-0.48}^{+0.63}$ & 0.04  \\
$\gamma\times0.1$          & $ 1.41_{-1.41}^{+7.58}$ & 0.58 & $ 1.34_{-1.34}^{+6.77}$ & 0.13  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Bouwens data with and without 
dust attenuation over 8 tiny boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Bouwens_best_fit_parameters_no_dust}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.07_{-0.06}^{+0.10}$ & 0.03 & $17.81_{-0.08}^{+0.12}$ & 0.02  \\
$\log_{10}(M_0/M_{\odot})$ & $11.19_{-0.03}^{+0.67}$ & 0.07 & $11.12_{-0.24}^{+0.58}$ & 0.06  \\
$\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
$\gamma\times10$           & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Willott data with and without 
dust attenuation over 64 small boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Willott_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.06 & $17.81_{-0.16}^{+0.22}$ & 0.07  \\
$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.13 & $11.82_{-0.32}^{+1.02}$ & 0.18  \\
$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.04 & $ 0.91_{-0.48}^{+0.63}$ & 0.11  \\
$\gamma\times10$           & $ 1.41_{-1.41}^{+7.58}$ & 1.34 & $ 1.34_{-1.34}^{+6.77}$ & 1.03  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Bouwens data with and without 
dust attenuation over 8 tiny boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Bouwens_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.03_{-0.20}^{+0.08}$ & 0.05 & $17.78_{-0.12}^{+0.15}$ & 0.07  \\
$\log_{10}(M_0/M_{\odot})$ & $11.41_{-0.83}^{+0.57}$ & 0.27 & $11.01_{-0.43}^{+0.83}$ & 0.40  \\
$\beta$                    & $ 0.49_{-0.44}^{+1.07}$ & 0.60 & $ 0.67_{-0.65}^{+0.90}$ & 0.64  \\
$\gamma\times10$           & $ 1.95_{-1.39}^{+2.93}$ & 2.43 & $ 3.36_{-1.06}^{+2.91}$ & 0.78  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the McLure data with and without 
dust attenuation over 8 tiny boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:McLure_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $17.98_{-0.07}^{+0.23}$ & 0.04 & $17.63_{-0.06}^{+0.17}$ & 0.01  \\
$\log_{10}(M_0/M_{\odot})$ & $11.17_{-0.10}^{+0.51}$ & 0.05 & $10.88_{-0.11}^{+0.44}$ & 0.05  \\
$\beta$                    & $ 1.36_{-0.48}^{+0.22}$ & 0.08 & $ 1.56_{-0.75}^{+0.03}$ & 0.04  \\
$\gamma\times10$           & $ 0.24_{-0.23}^{+5.03}$ & 0.20 & $ 0.93_{-0.83}^{+3.03}$ & 0.42  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Finkelstein data with and without 
dust attenuation over 8 tiny boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Finkelstein_best_fit_parameters_no_dust}
\end{center}
\end{table}
